---
title: 'Lab 2: Iterations with {purrr}'
author: "Cameron Kay & Ashley Miller"
date: "4/17/2019"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

## Part A: Multiple Models

Run the code below to load the following dataset.

```{r parta_load_data}
file <- "https://github.com/datalorax/esvis/raw/master/data/benchmarks.rda"
load(url(file))
head(benchmarks)
```

These data are simulated, but represent individual student scores across seasonal benchmark screenings (administered in the fall, winter, and spring). The variables are as follows:

  + sid: student identifier
  + cohort: student cohort
  + sped: special education status of the student for the given time point
  + ethnicity: coded race/ethnicity of the student
  + frl: free or reduced price lunch eligibility for the student for the given time point
  + ell: English language learner status for the student for the given time point
  + season: season the assessment was administered
  + reading: student’s reading score at the given time point
  + math: student’s mathematics score at the given time point
  
Recode season to wave with the following code

```{r parta_recode}
library(tidyverse)

benchmarks <- benchmarks %>%
    as_tibble() %>%
    mutate(wave = case_when(season == "Fall" ~ 0,
                            season == "Winter" ~ 1,
                            TRUE ~ 2))
```

### 1. Fit a model of the form lm(math ~ wave) for each student.

```{r parta_q1}

```

### 2. Plot the distribution of slopes for each student. Annotate the plot with a vertical line for the mean.

```{r parta_q2}

```

## Part B: Star Wars

Install and load the {repurrrsive} package.

```{r partb_load_data}
# install.packages("repurrrsive")
library(repurrrsive)
```

You now should have access to all the data you’ll need for the following.

### 1. Use the sw_films list to identify how many characters were represented in each film.

```{r partb_q1}

```

### 2. Use the sw_species list to (a) identify species that have known hair colors and (b) identify what those hair colors are

```{r partb_q2}
# extract names
sw_species_names <- map_chr(sw_species, "name")

# extract hair colours
sw_species_hair  <- map_chr(sw_species, "hair_colors")

# combine character vectors
sw_species_df <- tibble(sw_species_names,
                        sw_species_hair)

# filter non-n/a
sw_species_df %>%
  filter(sw_species_hair != "n/a",
         sw_species_hair != "none")
```

## Part C: Some basic API calls

Many of the list elements have urls for API calls. For example

```{r partc_url_example}
sw_films[[1]]$characters[1]
```

The above provides the url necessary to make an API call for all the information available on the first character in the first film. You can get this information into R with the following code

```{r partc_import_code}
library(httr)
char_1 <- GET(sw_films[[1]]$characters[1]) %>%
    content("parsed") 
```

You’ll note it looks very similar to the lists we’ve been working with. If you’re interested, you may want to actually visit the link in your browser. Essentially, the call requests that the API provide the output available for the first character. This is returned in JSON format, and the content(x, "parsed") part transforms it into a nested list.

### 1. Create a data frame that has two columns listing the names of every character in the first film (i.e., all the characters in sw_films[[1]]$characters), and the total number of films each character appeared in (note, this may take a minute or two).

```{r partc_q1}
# get character list
sw_films_list <- map(sw_films[[1]]$characters, function(url) {
  content(GET(url), "parsed")
})

# get character names
sw_films_names  <- map_chr(sw_films_list, ~.x$name)

# get character movies count
sw_films_movies <- map_int(sw_films_list, ~length(.x$films))

# create a datarame from the two columns
sw_films_df     <- data.frame(sw_films_names, sw_films_movies)

# look at the df
sw_films_df 
```

### 2. Add an additional column to your data frame that includes the names of all the films each character was in (BONUS).

```{r partc_q2}

```
